Paper Figure Generation

### 2023-11-27 R/PaperFigureGeneration.rmd
Added analysis with updated nucleosome map
- The previous nucleosome map (hg19_mnase_all) was not well documented. The new nucleosome map (hg19_LCL_mnase_all_mappable) has much clearer documentation on its origins.
- This new map also has blacklisted regions removed, using Dr. Wyrick's intersect_MNasenucs_Blacklist.pl script and the DAC_Duke_hg19_excludable regions, which were also added to the new "perl" directory.
- R scripts were also altered slightly to remove whitespace, standardize spacing after commas, etc.
- Lastly, a bug was discovered and fixed in the figure S16 generation code. (5'

---
title: "Paper Figure Generation"
author: "Ben Morledge-Hampton"
date: "6/21/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

@@

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
               fig.path = paste0(file.path("deamination_analysis_output","paper_figures"),
                                 .Platform$file.sep))

@@

```{r figure_5B, fig.width = 8, fig.height = 5}
NHF1TandemMismatchCountsComparisonAllReps = NHF1TandemMismatchCountsComparisonAllReps[
  Lesion == "CPD" & Timepoint == "1h"
]
print(
    ggplot(NHF1TandemMismatchCountsComparisonAllReps, aes(Mismatch_Type, Tandem_Mismatches_Count, fill = Search_Method)) +
      geom_bar(stat = "identity", position = "dodge") +
      labs(title = "NHF1 CPD 1h All Reps Tandem Mismatch Counts", x = "Mismatch Type", y = "Tandem Mismatch Count") +
      geom_text(aes(label=Tandem_Mismatches_Count), position = position_dodge(width = 0.9), vjust = -0.25, size = 5) +
      blankBackground + defaultTextScaling + scale_fill_brewer(palette = "Set1") +
      coord_cartesian(ylim = c(0,200000), expand = FALSE)
  )
```

@@

```{r read_figure_8_data}
NHF1NucleosomeRelativeCutSiteDistances = list(`1h` = NULL, `8h` = NULL)
for (i in seq_along(NHF1NucleosomeRelativeCutSiteDistances)) {
  NHF1NucleosomeRelativeCutSiteDistances[[i]] = list(three_prime = NULL, five_prime = NULL)
  NHF1NucleosomeRelativeCutSiteDistances[[i]]$three_prime = fread(generateFilePath(
    NHF1FeatureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv",
    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1NucleosomeRelativeCutSiteDistances)[i],
    strandPolarity = THREE_PRIME, repitition = "all_reps", filtering = "TGG_filtered",
    includedMismatches = "C>T", additionalInformation = "hg19_mnase_all_related_strand_aligned"
  ))
  NHF1NucleosomeRelativeCutSiteDistances[[i]]$five_prime = fread(generateFilePath(
    NHF1FeatureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv",
    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1NucleosomeRelativeCutSiteDistances)[i],
    strandPolarity = FIVE_PRIME, repitition = "all_reps", filtering = "TGG_filtered",
    includedMismatches = "C>T", additionalInformation = "hg19_mnase_all_related_strand_aligned"
  ))
}
```

```{r figure_8A, fig.width = 10, fig.height = 5}
plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`1h`$three_prime,
                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                          plotCutSiteSignificance = FALSE,
                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                          title = "NHF1 1h C>T All Reps TGG-Filtered Strand-Aligned",
                          xAxisLabel = "Dyad-Relative Position", xlim = c(-200, 200),
                          mainYAxisMin = 7.08, mainYAxisBreaks = seq(7.1,7.8,0.1),
                          secondaryAxisBreaks = seq(19,19.8,0.2),
                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
```
```{r figure_8B}
plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`1h`$three_prime,
                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                          title = "NHF1 1h C>T All Reps TGG-Filtered Strand-Aligned",
                          xAxisLabel = "Dyad-Relative Position", xlim = c(-100, -40),
                          mainYAxisMin = 7.08, mainYAxisBreaks = seq(7.1,7.8,0.1),
                          secondaryAxisBreaks = seq(19,19.8,0.2),
                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
```
```{r figure_8C}
plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`1h`$three_prime,
                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                          title = "NHF1 1h C>T All Reps TGG-Filtered Strand-Aligned",
                          xAxisLabel = "Dyad-Relative Position", xlim = c(40, 100),
                          mainYAxisMin = 7.08, mainYAxisBreaks = seq(7.1,7.8,0.1),
                          secondaryAxisBreaks = seq(19,19.8,0.2), 
                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
```

@@

```{r figure_S16A, fig.width = 10, fig.height = 5}
plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
                          plotCutSiteSignificance = FALSE,
                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                          title = "NHF1 8h C>T All Reps TGG-Filtered Strand-Aligned",
                          xAxisLabel = "Dyad-Relative Position", xlim = c(-200, 200),
                          secondaryAxisBreaks = seq(19,19.8,0.2),
                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
```
```{r figure_S16B}
plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                          title = "NHF1 8h C>T All Reps TGG-Filtered Strand-Aligned",
                          xAxisLabel = "Dyad-Relative Position", xlim = c(-100, -40),
                          secondaryAxisBreaks = seq(19,19.8,0.2),
                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
```
```{r figure_S16C}
plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                          title = "NHF1 8h C>T All Reps TGG-Filtered Strand-Aligned",
                          xAxisLabel = "Dyad-Relative Position", xlim = c(40, 100),
                          secondaryAxisBreaks = seq(19,19.8,0.2),
                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
```

>>>>

---
title: "Paper Figure Generation"
author: "Ben Morledge-Hampton"
date: "6/21/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: ~/bioinformatics
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects, ~/bioinformatics]
---

@@

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5,
               fig.path = paste0(file.path("deamination_analysis_output", "paper_figures"),
                                 .Platform$file.sep))

@@

```{r figure_5B, fig.width = 8, fig.height = 5}
NHF1TandemMismatchCountsComparisonAllReps = NHF1TandemMismatchCountsComparisonAllReps[
  Lesion == "CPD" & Timepoint == "1h"
]
print(
    ggplot(NHF1TandemMismatchCountsComparisonAllReps, aes(Mismatch_Type, Tandem_Mismatches_Count, fill = Search_Method)) +
      geom_bar(stat = "identity", position = "dodge") +
      labs(title = "NHF1 CPD 1h All Reps Tandem Mismatch Counts", x = "Mismatch Type", y = "Tandem Mismatch Count") +
      geom_text(aes(label = Tandem_Mismatches_Count), position = position_dodge(width = 0.9), vjust = -0.25, size = 5) +
      blankBackground + defaultTextScaling + scale_fill_brewer(palette = "Set1") +
      coord_cartesian(ylim = c(0,200000), expand = FALSE)
  )
```

@@

```{r read_figure_8_data}
NHF1NucleosomeRelativeCutSiteDistances = list(hg19_LCL_mnase_all_mappable = NULL)
for (j in seq_along(NHF1NucleosomeRelativeCutSiteDistances)) {
  NHF1NucleosomeRelativeCutSiteDistances[[j]] = list(`1h` = NULL, `8h` = NULL)
  for (i in seq_along(NHF1NucleosomeRelativeCutSiteDistances[[j]])) {
    NHF1NucleosomeRelativeCutSiteDistances[[j]][[i]] = list(three_prime = NULL, five_prime = NULL)
    NHF1NucleosomeRelativeCutSiteDistances[[j]][[i]]$three_prime = fread(generateFilePath(
      NHF1FeatureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv",
      cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1NucleosomeRelativeCutSiteDistances[[j]])[i],
      strandPolarity = THREE_PRIME, repitition = "all_reps", filtering = "TGG_filtered",
      includedMismatches = "C>T", additionalInformation = paste0(names(NHF1NucleosomeRelativeCutSiteDistances)[j],
                                                                 "_related_strand_aligned")
    ))
    NHF1NucleosomeRelativeCutSiteDistances[[j]][[i]]$five_prime = fread(generateFilePath(
      NHF1FeatureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv",
      cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1NucleosomeRelativeCutSiteDistances[[j]])[i],
      strandPolarity = FIVE_PRIME, repitition = "all_reps", filtering = "TGG_filtered",
      includedMismatches = "C>T", additionalInformation = paste0(names(NHF1NucleosomeRelativeCutSiteDistances)[j],
                                                                 "_related_strand_aligned")
    ))
  }
}
```

```{r figure_8A, fig.width = 10, fig.height = 5}
for (i in seq_along(NHF1NucleosomeRelativeCutSiteDistances)) {
  plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances[[i]]$`1h`$three_prime,
                            FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                            plotCutSiteSignificance = FALSE,
                            countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                            meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances[[i]]$`1h`$five_prime,
                            cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                            title = "NHF1 1h C>T All Reps TGG-Filtered Strand-Aligned",
                            xAxisLabel = "Dyad-Relative Position", xlim = c(-200, 200),
                            mainYAxisMin = 7.08, mainYAxisBreaks = seq(7.1,7.8,0.1),
                            secondaryAxisBreaks = seq(19,19.8,0.2),
                            meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975,
                            markFirstNucleosomeBoundaries = TRUE)
}
```
```{r figure_8B}
for (i in seq_along(NHF1NucleosomeRelativeCutSiteDistances)) {
  plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances[[i]]$`1h`$three_prime,
                            FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                            countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                            meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances[[i]]$`1h`$five_prime,
                            cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                            title = "NHF1 1h C>T All Reps TGG-Filtered Strand-Aligned",
                            xAxisLabel = "Dyad-Relative Position", xlim = c(-100, -40),
                            mainYAxisMin = 7.08, mainYAxisBreaks = seq(7.1,7.8,0.1),
                            secondaryAxisBreaks = seq(19,19.8,0.2),
                            meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
}
```
```{r figure_8C}
for (i in seq_along(NHF1NucleosomeRelativeCutSiteDistances)) {
  plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances[[i]]$`1h`$three_prime,
                            FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                            countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                            meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances[[i]]$`1h`$five_prime,
                            cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                            title = "NHF1 1h C>T All Reps TGG-Filtered Strand-Aligned",
                            xAxisLabel = "Dyad-Relative Position", xlim = c(40, 100),
                            mainYAxisMin = 7.08, mainYAxisBreaks = seq(7.1,7.8,0.1),
                            secondaryAxisBreaks = seq(19,19.8,0.2),
                            meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
}
```

@@

```{r figure_S16A, fig.width = 10, fig.height = 5}
for (i in seq_along(NHF1NucleosomeRelativeCutSiteDistances)) {
  plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances[[i]]$`8h`$three_prime,
                            plotCutSiteSignificance = FALSE,
                            FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                            countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                            meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances[[i]]$`8h`$five_prime,
                            cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                            title = "NHF1 8h C>T All Reps TGG-Filtered Strand-Aligned",
                            xAxisLabel = "Dyad-Relative Position", xlim = c(-200, 200),
                            secondaryAxisBreaks = seq(19,19.8,0.2),
                            meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975,
                            markFirstNucleosomeBoundaries = TRUE)
}
```
```{r figure_S16B}
for (i in seq_along(NHF1NucleosomeRelativeCutSiteDistances)) {
  plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances[[i]]$`8h`$three_prime,
                            FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                            countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                            meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances[[i]]$`8h`$five_prime,
                            cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                            title = "NHF1 8h C>T All Reps TGG-Filtered Strand-Aligned",
                            xAxisLabel = "Dyad-Relative Position", xlim = c(-100, -40),
                            secondaryAxisBreaks = seq(19,19.8,0.2),
                            meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
}
```
```{r figure_S16C}
for (i in seq_along(NHF1NucleosomeRelativeCutSiteDistances)) {
  plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances[[i]]$`8h`$three_prime,
                            FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                            countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                            meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances[[i]]$`8h`$five_prime,
                            cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                            title = "NHF1 8h C>T All Reps TGG-Filtered Strand-Aligned",
                            xAxisLabel = "Dyad-Relative Position", xlim = c(40, 100),
                            secondaryAxisBreaks = seq(19,19.8,0.2),
                            meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
}
```
